SimSurvey demo

### 2025-01-31 tutorial/tutorial.Rmd
Minor tweak of tutorial

## Make mesh and fit geostatistical model to survey data
mesh <- sdmTMB::make_mesh(dat, xy_cols = c("x", "y"), cutoff = 20)
fit <- sdmTMB(N ~ 0 + as.factor(year) + offset,
              data = dat,
              family = nbinom2(link = "log"), spde = mesh,
              include_spatial = TRUE, time = "year")

>>>>

## Make mesh and fit geostatistical model to survey data
mesh <- sdmTMB::make_mesh(dat, xy_cols = c("x", "y"), cutoff = 20)
fit <- sdmTMB(N ~ 0 + as.factor(year),
              offset = dat$offset,
              mesh = mesh,
              data = dat,
              family = nbinom2(link = "log"), 
              time = "year")
